---
title: "Mediation analysis"
author: "Kate Tran"
date: "3/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(readxl)
library(lavaan)
library(lavaanPlot)
library(tidyr)
library(DiagrammeRsvg)
library(rsvg)
library(readr)
library(sjPlot)

# save.image("~/Documents/KateTran_Github/ABCD_covid/ABCD_covid_mediation_analysis_final.RData")
```

```{r}
# Read data from mixed model final long data
covidp_long <- read.csv("~/Documents/KateTran_Github/ABCD_covid/outputs_Kate/covidp_long.csv")
covidy_long <- read.csv("~/Documents/KateTran_Github/ABCD_covid/outputs_Kate/covidy_long.csv")
family_ <- read.csv("~/Documents/KateTran_Github/ABCD_covid/outputs_Kate/family.csv") %>%
  dplyr::select(-eventname)
demo_baseline <- read.csv("~/Documents/KateTran_Github/ABCD_covid/outputs_Kate/demographics_baseline.csv")
demographics_long <- read.csv("~/Documents/KateTran_Github/ABCD_covid/outputs_Kate/demographics_long.csv")
exposome_sum_set <- read.csv("~/Documents/KateTran_Github/ABCD_covid/outputs_Kate/exposome_sum_set.csv")
p_factor_with_sui <- 
  read_csv("~/Library/CloudStorage/Box-Box/2-ABCD Data Files/Projects/exposome/3.0/data/p factor scores/ABCD_psychopathology_bifactor_scores_23March2021_WITH_SUICIDALITY.csv")

p_factor_with_sui$src_subject_id <- paste0("NDAR_", p_factor_with_sui$ID)
p_factor_with_sui$ID <- NULL
colnames(p_factor_with_sui)[1:7] <- paste0(colnames(p_factor_with_sui)[1:7], "_with_sui")


IVs <- merge(demographics_long, exposome_sum_set, all = T)
IVs <- IVs[(IVs$eventname == "1_year_follow_up_y_arm_1"),]

colnames(IVs)[2] <- "interview_date_before_covid"
colnames(IVs)[3] <- "interview_age_before_covid"
IVs$eventname <- NULL


covid_long_mixed_model <- merge(covidp_long, covidy_long, all = T)
covid_long_mixed_model <- merge(covid_long_mixed_model, family_, all.x = T)
covid_long_mixed_model <- merge(covid_long_mixed_model, IVs)

covid_long_mixed_model <- covid_long_mixed_model %>%
  dplyr::mutate(timepoint = sub("cv", "" , timepoint)) %>%
  dplyr::select(-eventname,-contains("fam_actions_cv"))

# to wide format
covid_wide <- covid_long_mixed_model %>%
  pivot_wider(
    .,
    names_from = timepoint,
    values_from = c(
      fam_exp_racism_cv:pstr_cv_raw_tot_bar.1,
      ends_with("_l"), interview_age,
      stq_y_ss_weekday:dim_y_ss_mean
    ),
    names_sep = "_"
  ) %>%
  dplyr::select(
    -sex,
    -household_income,
    -parents_avg_edu,
    -separated_or_divorced,
    -parents_married,
    -age,
    -sex_br,
    -gender,
    -demo_fam_poverty
  )

demo_baseline[, c("interview_date" , "interview_age" , "eventname")] <- NULL
covid_wide <- merge(covid_wide, demo_baseline, all.x = T)

covid_wide$rel_family_id <- covid_wide$rel_family_id + 1


covid_wide <- merge(covid_wide, p_factor_with_sui, all.x = T)
```

# Create the wide format

```{r}
covid_wide <- covid_wide %>%
  dplyr::select(
    # IV
    fam_wage_loss_cv_1,
    fam_wage_loss_cv_2,
    fam_wage_loss_cv_3,
    fam_wage_loss_cv_4,
    fam_wage_loss_cv_5,
    fam_wage_loss_cv_6,
    fam_wage_loss_cv_7,
    # M
    increased_conflict_cv_1,
    increased_conflict_cv_3,
    increased_conflict_cv_5,
    # M
    work_ability_cv_1,
    work_ability_cv_2,
    work_ability_cv_3,
    work_ability_cv_4,
    work_ability_cv_5,
    work_ability_cv_6,
    work_ability_cv_7,
    # M
    parent_monitor_tot_bar_1,
    parent_monitor_tot_bar_2,
    parent_monitor_tot_bar_3,
    parent_monitor_tot_bar_4,
    parent_monitor_tot_bar_5,
    parent_monitor_tot_bar_6,
    parent_monitor_tot_bar_7,
    # DV felt_sad_cv_raw_tot_bar_Z
    felt_sad_cv_raw_tot_bar_1,
    felt_sad_cv_raw_tot_bar_2,
    felt_sad_cv_raw_tot_bar_3,
    felt_sad_cv_raw_tot_bar_4,
    felt_sad_cv_raw_tot_bar_5,
    felt_sad_cv_raw_tot_bar_6,
    felt_sad_cv_raw_tot_bar_7,
    ## money worries
    money_cv_1,
    money_cv_2,
    money_cv_3,
    money_cv_4,
    money_cv_5,
    money_cv_6,
    money_cv_7,
    
    ## discrimination
    dim_y_ss_mean_1,
    dim_y_ss_mean_2,
    dim_y_ss_mean_3,
    dim_y_ss_mean_4,
    dim_y_ss_mean_5,
    dim_y_ss_mean_6,
    dim_y_ss_mean_7,
    
    # Covariates
    sex_br,
    race_white,
    race_black,
    race_asian,
    ethnicity_hisp,
    household_income,
    parents_avg_edu,
    contains("mean"),
    interview_age_1,
    interview_age_2,
    interview_age_3,
    interview_age_4,
    interview_age_5,
    interview_age_6,
    interview_age_7,
    
    # General_p_with_sui
    General_p_with_sui
  )


covid_wide <- covid_wide %>%
  rowwise() %>%
  # Create new variables for mediation model
  dplyr::mutate(
    # Summary of IV at t1 and t2, if any = 1 then 1, both 0 then 0, 1NA then NA
    fam_wage_loss_cv_mean12 = case_when(
      fam_wage_loss_cv_1 == 1 | fam_wage_loss_cv_2 == 1 ~ 1,
      fam_wage_loss_cv_1 == 0 & fam_wage_loss_cv_2 == 0 ~ 0,
      is.na(fam_wage_loss_cv_1) &
        fam_wage_loss_cv_2 == 0  ~ NA_real_,
      is.na(fam_wage_loss_cv_2) &
        fam_wage_loss_cv_1 == 0  ~ NA_real_,
      is.na(fam_wage_loss_cv_1) &
        is.na(fam_wage_loss_cv_2) ~ NA_real_
    )
  ) %>%
  dplyr::mutate(
    # Summary of moderators t3&t5 or t3-t6 mean
    ## increased_conflict_cv
    increased_conflict_cv_mean35 = mean(c(
      increased_conflict_cv_3, increased_conflict_cv_5
    ), na.rm = TRUE),
    
    ## work_ability_cv
    work_ability_cv_mean3to6 = mean(
      c(
        work_ability_cv_3,
        work_ability_cv_4,
        work_ability_cv_5,
        work_ability_cv_6
      ),
      na.rm = TRUE
    ),
    
    ## parent_monitor_tot_bar
    parent_monitor_tot_bar_cv_mean3to6 = mean(
      c(
        parent_monitor_tot_bar_3,
        parent_monitor_tot_bar_4,
        parent_monitor_tot_bar_5,
        parent_monitor_tot_bar_6
      ),
      na.rm = TRUE
    ),
    
    ## worries about money T3, T4, T5
    money_cv_mean345 = mean(c(money_cv_3, money_cv_4, money_cv_5), na.rm = TRUE),
    
    ## DV mean T5 and T7
    felt_sad_cv_raw_tot_bar_mean57 = mean(
      c(felt_sad_cv_raw_tot_bar_5, felt_sad_cv_raw_tot_bar_7),
      na.rm = TRUE
    ),
    
    ## Discrimination mean 7 time points
    dim_y_ss_mean = mean(
      c(
        dim_y_ss_mean_1,
        dim_y_ss_mean_2,
        dim_y_ss_mean_3,
        dim_y_ss_mean_4,
        dim_y_ss_mean_5,
        dim_y_ss_mean_6,
        dim_y_ss_mean_7
      ),
      na.rm = TRUE
    ),
    
    ## Age at interview mean
    age_mean_cv = mean(
      c(
        interview_age_1,
        interview_age_2,
        interview_age_3,
        interview_age_4,
        interview_age_5,
        interview_age_6,
        interview_age_7
      ),
      na.rm = TRUE
    )
  ) 





# Add variables
covid_wide <- covid_wide %>%
  rowwise() %>%
  dplyr::mutate(
    ## work_ability_cv T3-5
    work_ability_cv_mean3to5 = mean(
      c(work_ability_cv_3, work_ability_cv_4, work_ability_cv_5),
      na.rm = TRUE
    ),
    
    ## parent_monitor_tot_bar T3-5
    parent_monitor_tot_bar_cv_mean3to5 = mean(
      c(
        parent_monitor_tot_bar_3,
        parent_monitor_tot_bar_4,
        parent_monitor_tot_bar_5
      ),
      na.rm = TRUE
    ),
  )

covid_wide <- covid_wide %>%
  rowwise() %>%
  dplyr::mutate(## worries about money T3, T4, T5
    money_cv_mean3to6 = mean(c(
      money_cv_3, money_cv_4, money_cv_5, money_cv_6
    ), na.rm = TRUE))

covid_wide <- covid_wide %>%
dplyr::mutate(across(c(
  fam_wage_loss_cv_mean12,
  sex_br,
  race_white,
  race_black,
  race_asian,
  ethnicity_hisp
)))

# writexl::write_xlsx(covid_wide, "~/Documents/KateTran_Github/ABCD_covid/outputs_Kate/mediation_dat_final.xlsx")
```

# 1. MEDIATOR WORRIES ABOUT MONEY

```{r}
mod_mean_money <- '
money_cv_mean3to6 ~ a*fam_wage_loss_cv_mean12
felt_sad_cv_raw_tot_bar_7 ~ c*fam_wage_loss_cv_mean12 + b*money_cv_mean3to6
ind := a*b
total := c + a*b
'

med_mod_mean_money <- lavaan::sem(mod_mean_money,
                                  data = covid_wide,
                                  se = "bootstrap",
                                  bootstrap = 500)

med_mod_mean_money_sum <- parameterEstimates(
  med_mod_mean_money,
  ci = TRUE,
  level = 0.95,
  boot.ci.type = "perc"
)


labels_mean_money = list(
  fam_wage_loss_cv_mean12 = "Wage loss T1-2 \n (independent variable)",
  felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)",
  money_cv_mean3to6 = "Worries about money T3-4-5-6 \n (mediator)"
)

plot_mean_money <- lavaanPlot(
  model = med_mod_mean_money,
  labels = labels_mean_money,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(
  plot_mean_money,
  "~/Documents/KateTran_Github/ABCD_covid/plots/plot_mean_money.png"
)
```

### Simple linear regression with covariates

```{r}
model_1_sl_cov <- '
felt_sad_cv_raw_tot_bar_7 ~ 1 + fam_wage_loss_cv_mean12 + age_mean_cv + sex_br + race_white + race_black + race_asian + ethnicity_hisp
'

med_model_1_sl_cov <- lavaan::sem(model_1_sl_cov,
                                  data = covid_wide,
                                  se = "bootstrap",
                                  bootstrap = 500)

med_model_1_sl_cov_sum <- parameterEstimates(
  med_model_1_sl_cov,
  ci = TRUE,
  level = 0.95,
  boot.ci.type = "perc"
)

labels_1_sl_cov = list(fam_wage_loss_cv_mean12 = "Wage loss T1-2 \n (independent variable)",
                       felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)")

plot_1_sl_cov <- lavaanPlot(
  model = med_model_1_sl_cov,
  labels = labels_1_sl_cov,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(plot_1_sl_cov,
         "~/Documents/KateTran_Github/ABCD_covid/plots/plot_1_sl_cov.png")
```


```{r}
model_1_sl_cov_p <- '
felt_sad_cv_raw_tot_bar_7 ~ 1 + fam_wage_loss_cv_mean12 + age_mean_cv + sex_br + race_white + race_black + race_asian + ethnicity_hisp +
household_income + parents_avg_edu + General_p_with_sui + dim_y_ss_mean
'

med_model_1_sl_cov_p <- lavaan::sem(model_1_sl_cov_p,
                                    data = covid_wide,
                                    se = "bootstrap",
                                    bootstrap = 500)

med_model_1_sl_cov_p_sum <- parameterEstimates(
  med_model_1_sl_cov_p,
  ci = TRUE,
  level = 0.95,
  boot.ci.type = "perc"
)

labels_1_sl_cov_p = list(fam_wage_loss_cv_mean12 = "Wage loss T1-2 \n (independent variable)",
                         felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)")

plot_1_sl_cov_p <- lavaanPlot(
  model = med_model_1_sl_cov_p,
  labels = labels_1_sl_cov,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(
  plot_1_sl_cov_p,
  "~/Documents/KateTran_Github/ABCD_covid/plots/plot_1_sl_cov_p.png"
)
```

For the next analysis, DV will be at time point 7 (cannot do mean 5&7 because no observations of conflict at T4)

# 2. MEDIATOR FAMILIES' PROBLEMS

### M1: Family conflict

```{r}
mod_mean_M1 <- '
increased_conflict_cv_mean35 ~ a*fam_wage_loss_cv_mean12
felt_sad_cv_raw_tot_bar_7 ~ c*fam_wage_loss_cv_mean12 + b*increased_conflict_cv_mean35
ind := a*b
total := c + a*b
'

med_mod_mean_M1 <- lavaan::sem(mod_mean_M1,
                               data = covid_wide,
                               se = "bootstrap",
                               bootstrap = 500)

med_mod_mean_M1_sum <- parameterEstimates(
  med_mod_mean_M1,
  ci = TRUE,
  level = 0.95,
  boot.ci.type = "perc"
)

labels_mean_M1 = list(
  fam_wage_loss_cv_mean12 = "Wage loss T1-2 \n (independent variable)",
  felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)",
  increased_conflict_cv_mean35 = "Family conflict T3-5 \n (mediator)"
)

plot_mean_M1 <- lavaanPlot(
  model = med_mod_mean_M1,
  labels = labels_mean_M1,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(
  plot_mean_M1,
  "~/Documents/KateTran_Github/ABCD_covid/plots/mediator_parentsconflict/plot_mean_M1.png"
)
```


### M2: Parent monitoring

```{r}
mod_mean_M2 <- '
parent_monitor_tot_bar_cv_mean3to6 ~ a*fam_wage_loss_cv_mean12
felt_sad_cv_raw_tot_bar_7 ~ c*fam_wage_loss_cv_mean12 + b*parent_monitor_tot_bar_cv_mean3to6
ind := a*b
total := c + a*b
'

med_mod_mean_M2 <- lavaan::sem(mod_mean_M2,
                               data = covid_wide,
                               se = "bootstrap",
                               bootstrap = 500)

med_mod_mean_M2_sum <- parameterEstimates(
  med_mod_mean_M2,
  ci = TRUE,
  level = 0.95,
  boot.ci.type = "perc"
)

labels_mean_M2 = list(
  fam_wage_loss_cv_mean12 = "Wage loss T1-2 \n (independent variable)",
  felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)",
  parent_monitor_tot_bar_cv_mean3to6 = "Parent monitoring T3-4-5-6 \n (mediator)"
)

plot_mean_M2 <- lavaanPlot(
  model = med_mod_mean_M2,
  labels = labels_mean_M2,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(
  plot_mean_M2,
  "~/Documents/KateTran_Github/ABCD_covid/plots/mediator_parentsconflict/plot_mean_M2.png"
)
```


### M3: Parent workplace conflict

```{r}
mod_mean_M3 <- '
work_ability_cv_mean3to6 ~ a*fam_wage_loss_cv_mean12
felt_sad_cv_raw_tot_bar_7 ~ c*fam_wage_loss_cv_mean12 + b*work_ability_cv_mean3to6
ind := a*b
total := c + a*b
'

med_mod_mean_M3 <- lavaan::sem(mod_mean_M3,
                               data = covid_wide,
                               se = "bootstrap",
                               bootstrap = 500)

med_mod_mean_M3_sum <- parameterEstimates(
  med_mod_mean_M3,
  ci = TRUE,
  level = 0.95,
  boot.ci.type = "perc"
)

labels_mean_M3 = list(
  fam_wage_loss_cv_mean12 = "Wage loss T1-2 \n (independent variable)",
  felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)",
  work_ability_cv_mean3to6 = "Parent workplace conflict T3-4-5-6 \n (mediator)"
)

plot_mean_M3 <- lavaanPlot(
  model = med_mod_mean_M3,
  labels = labels_mean_M3,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(
  plot_mean_M3,
  "~/Documents/KateTran_Github/ABCD_covid/plots/mediator_parentsconflict/plot_mean_M3.png"
)
```

### M1 + M2 + M3 in the same plot

```{r}
model_1_mean_M1M2M3 <- '
increased_conflict_cv_mean35 ~ fc1*fam_wage_loss_cv_mean12
parent_monitor_tot_bar_cv_mean3to6 ~ pm1*fam_wage_loss_cv_mean12
work_ability_cv_mean3to6 ~ pwc1*fam_wage_loss_cv_mean12
felt_sad_cv_raw_tot_bar_7 ~ mf*fam_wage_loss_cv_mean12 + fc2*increased_conflict_cv_mean35 + pm2*parent_monitor_tot_bar_cv_mean3to6 + pwc2*work_ability_cv_mean3to6
increased_conflict_cv_mean35 ~~ parent_monitor_tot_bar_cv_mean3to6
parent_monitor_tot_bar_cv_mean3to6 ~~ work_ability_cv_mean3to6
work_ability_cv_mean3to6 ~~ increased_conflict_cv_mean35
indM1 := fc1*fc2
indM2 := pm1*pm2
indM3 := pwc1*pwc2
totalindirecteffect := fc1*fc2 + pm1*pm2 + pwc1*pwc2
totaleffect := mf + fc1*fc2 + pm1*pm2 + pwc1*pwc2
'

med_model_1_mean_M1M2M3 <- lavaan::sem(
  model_1_mean_M1M2M3,
  data = covid_wide,
  se = "bootstrap",
  bootstrap = 500
)

med_model_1_mean_M1M2M3_sum <-
  parameterEstimates(
    med_model_1_mean_M1M2M3,
    ci = TRUE,
    level = 0.95,
    boot.ci.type = "perc"
  )


labels_1_mean_M1M2M3 = list(
  increased_conflict_cv_mean35 = "Parent conflict T3-5 \n (mediator 1)",
  fam_wage_loss_cv_mean12 = "Wage loss T1-2 \n (independent variable)",
  parent_monitor_tot_bar_cv_mean3to6 = "Parent monitoring T3-4-5-6 \n (mediator 2)",
  work_ability_cv_mean3to6 = "Parent-workplace conflict T3-4-5-6 \n (mediator 3)",
  felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)"
)

plot_mean_M1M2M3 <- lavaanPlot(
  model = med_model_1_mean_M1M2M3,
  labels = labels_1_mean_M1M2M3,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  # covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(
  plot_mean_M1M2M3,
  "~/Documents/KateTran_Github/ABCD_covid/plots/mediator_parentsconflict/plot_mean_M1M2M3.png"
)
```

### M1 + M2 + M3 + M4 (worries about money) in the same plot

```{r}
# Add worries about money
model_1_mean_M1M2M3M4 <- '
increased_conflict_cv_mean35 ~ fc1*fam_wage_loss_cv_mean12
parent_monitor_tot_bar_cv_mean3to6 ~ pm1*fam_wage_loss_cv_mean12
work_ability_cv_mean3to6 ~ pwc1*fam_wage_loss_cv_mean12
money_cv_mean3to6 ~ mw1*fam_wage_loss_cv_mean12
felt_sad_cv_raw_tot_bar_7 ~ mf*fam_wage_loss_cv_mean12 + fc2*increased_conflict_cv_mean35 + pm2*parent_monitor_tot_bar_cv_mean3to6 +
pwc2*work_ability_cv_mean3to6 + mw2*money_cv_mean3to6
increased_conflict_cv_mean35 ~~ parent_monitor_tot_bar_cv_mean3to6
parent_monitor_tot_bar_cv_mean3to6 ~~ work_ability_cv_mean3to6
work_ability_cv_mean3to6 ~~ increased_conflict_cv_mean35
money_cv_mean3to6 ~~ increased_conflict_cv_mean35
money_cv_mean3to6 ~~ parent_monitor_tot_bar_cv_mean3to6
money_cv_mean3to6 ~~ work_ability_cv_mean3to6
indM1 := fc1*fc2
indM2 := pm1*pm2
indM3 := pwc1*pwc2
indM4 := mw1*mw2

totalindirecteffect := fc1*fc2 + pm1*pm2 + pwc1*pwc2 + mw1*mw2
totaleffect := mf + fc1*fc2 + pm1*pm2 + pwc1*pwc2 + mw1*mw2
'

med_model_1_mean_M1M2M3M4 <- lavaan::sem(
  model_1_mean_M1M2M3M4,
  data = covid_wide,
  se = "bootstrap",
  bootstrap = 500
)

med_model_1_mean_M1M2M3M4_sum <-
  parameterEstimates(
    med_model_1_mean_M1M2M3M4,
    ci = TRUE,
    level = 0.95,
    boot.ci.type = "perc"
  )

labels_1_mean_M1M2M3M4 = list(
  increased_conflict_cv_mean35 = "Parent conflict T3-5 \n (mediator 1)",
  fam_wage_loss_cv_mean12 = "Wage loss T1-2 \n (independent variable)",
  parent_monitor_tot_bar_cv_mean3to6 = "Parent monitoring T3-4-5-6 \n (mediator 2)",
  work_ability_cv_mean3to6 = "Parent-workplace conflict T3-4-5-6 \n (mediator 3)",
  money_cv_mean3to6 = "Worries about money T3-4-5-6 \n (mediator 4)",
  felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)"
)

plot_mean_M1M2M3M4 <- lavaanPlot(
  model = med_model_1_mean_M1M2M3M4,
  labels = labels_1_mean_M1M2M3M4,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  # covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(
  plot_mean_M1M2M3M4,
  "~/Documents/KateTran_Github/ABCD_covid/plots/mediator_parentsconflict/plot_mean_M1M2M3M4.png"
)
```

# 3. LONGITUDINAL MEDIATORS
## 3.1. M1 + M2 + M3

```{r}
model_2_long_M1M2M3 <- '
increased_conflict_cv_mean35 ~ fc1*fam_wage_loss_cv_1 + fc2*fam_wage_loss_cv_2
parent_monitor_tot_bar_cv_mean3to6 ~ pm1*fam_wage_loss_cv_1 + pm2*fam_wage_loss_cv_2
work_ability_cv_mean3to6 ~ pwc1*fam_wage_loss_cv_1 + pwc2*fam_wage_loss_cv_2
fam_wage_loss_cv_2 ~ wl1*fam_wage_loss_cv_1
felt_sad_cv_raw_tot_bar_7 ~ mf*fam_wage_loss_cv_1 + fc3*increased_conflict_cv_mean35 + pm3*parent_monitor_tot_bar_cv_mean3to6 + pwc3*work_ability_cv_mean3to6
increased_conflict_cv_mean35 ~~ parent_monitor_tot_bar_cv_mean3to6
parent_monitor_tot_bar_cv_mean3to6 ~~ work_ability_cv_mean3to6
work_ability_cv_mean3to6 ~~ increased_conflict_cv_mean35
indM1 := fc1*fc3 + wl1*fc2*fc3
indM2 := pm1*pm3 + wl1*pm2*pm3
indM3 := pwc1*pwc3 + wl1*pwc2*pwc3
totalindirecteffect := fc1*fc3 + wl1*fc2*fc3 + pm1*pm3 + wl1*pm2*pm3 + pwc1*pwc3 + wl1*pwc2*pwc3
totaleffect := mf + fc1*fc3 + wl1*fc2*fc3 + pm1*pm3 + wl1*pm2*pm3 + pwc1*pwc3 + wl1*pwc2*pwc3
'

med_model_2_long_M1M2M3 <- lavaan::sem(
  model_2_long_M1M2M3,
  data = covid_wide,
  se = "bootstrap",
  bootstrap = 500
)

med_model_2_long_M1M2M3_sum <-
  parameterEstimates(
    med_model_2_long_M1M2M3,
    ci = TRUE,
    level = 0.95,
    boot.ci.type = "perc"
  )


labels_long_M1M2M3 = list(
  increased_conflict_cv_mean35 = "Parent conflict \n (mediator 2)",
  fam_wage_loss_cv_1 = "Wage loss at T1 \n (independent variable)",
  fam_wage_loss_cv_2 = "Wage loss at T2 \n (mediator 1)",
  parent_monitor_tot_bar_cv_mean3to6 = "Parent monitoring T3-4-5-6 \n (mediator 3)",
  work_ability_cv_mean3to6 = "Parent-workplace conflict T3-4-5-6 \n (mediator 4)",
  felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)"
)

plot_long_M1M2M3 <- lavaanPlot(
  model = med_model_2_long_M1M2M3,
  labels = labels_long_M1M2M3,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  # covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(
  plot_long_M1M2M3,
  "~/Documents/KateTran_Github/ABCD_covid/plots/mediator_longitudinal/plot_long_M1M2M3.png"
)
```


## 3.2. M1 + M2 + M3 + M4

```{r}
model_2_long_M1M2M3M4 <- '
increased_conflict_cv_mean35 ~ fc1*fam_wage_loss_cv_1 + fc2*fam_wage_loss_cv_2
parent_monitor_tot_bar_cv_mean3to6 ~ pm1*fam_wage_loss_cv_1 + pm2*fam_wage_loss_cv_2
work_ability_cv_mean3to6 ~ pwc1*fam_wage_loss_cv_1 + pwc2*fam_wage_loss_cv_2
money_cv_mean3to6 ~ mw1*fam_wage_loss_cv_1 + mw2*fam_wage_loss_cv_2
fam_wage_loss_cv_2 ~ wl1*fam_wage_loss_cv_1
felt_sad_cv_raw_tot_bar_7 ~ mf*fam_wage_loss_cv_1 + fc3*increased_conflict_cv_mean35 + pm3*parent_monitor_tot_bar_cv_mean3to6 +
pwc3*work_ability_cv_mean3to6 + mw3*money_cv_mean3to6
increased_conflict_cv_mean35 ~~ parent_monitor_tot_bar_cv_mean3to6
parent_monitor_tot_bar_cv_mean3to6 ~~ work_ability_cv_mean3to6
work_ability_cv_mean3to6 ~~ increased_conflict_cv_mean35
money_cv_mean3to6 ~~ increased_conflict_cv_mean35
money_cv_mean3to6 ~~ parent_monitor_tot_bar_cv_mean3to6
money_cv_mean3to6 ~~ work_ability_cv_mean3to6
indM1 := fc1*fc3 + wl1*fc2*fc3
indM2 := pm1*pm3 + wl1*pm2*pm3
indM3 := pwc1*pwc3 + wl1*pwc2*pwc3
indM4 := mw1*mw3 + wl1*mw2*mw3
totalindirecteffect := fc1*fc3 + wl1*fc2*fc3 + pm1*pm3 + wl1*pm2*pm3 + pwc1*pwc3 + wl1*pwc2*pwc3 + mw1*mw3 + wl1*mw2*mw3
totaleffect := mf + fc1*fc3 + wl1*fc2*fc3 + pm1*pm3 + wl1*pm2*pm3 + pwc1*pwc3 + wl1*pwc2*pwc3 + mw1*mw3 + wl1*mw2*mw3
'

med_model_2_long_M1M2M3M4 <- lavaan::sem(
  model_2_long_M1M2M3M4,
  data = covid_wide,
  se = "bootstrap",
  bootstrap = 500
)

med_model_2_long_M1M2M3M4_sum <-
  parameterEstimates(
    med_model_2_long_M1M2M3M4,
    ci = TRUE,
    level = 0.95,
    boot.ci.type = "perc"
  )


labels_long_M1M2M3M4 = list(
  increased_conflict_cv_mean35 = "Parent conflict \n (mediator 2)",
  fam_wage_loss_cv_1 = "Wage loss at T1 \n (independent variable)",
  fam_wage_loss_cv_2 = "Wage loss at T2 \n (mediator 1)",
  parent_monitor_tot_bar_cv_mean3to6 = "Parent monitoring T3-4-5-6 \n (mediator 3)",
  work_ability_cv_mean3to6 = "Parent-workplace conflict T3-4-5-6 \n (mediator 4)",
  felt_sad_cv_raw_tot_bar_7 = "Mental health problem T7 \n (outcome)",
  money_cv_mean3to6 = "Worries about money T3-4-5-6 \n (mediator 5)"
)

plot_long_M1M2M3M4 <- lavaanPlot(
  model = med_model_2_long_M1M2M3M4,
  labels = labels_long_M1M2M3M4,
  node_options = list(
    shape = "box",
    fontname = "Arial",
    color = "blue4"
  ),
  edge_options = list(color = "darkolivegreen"),
  coefs = TRUE,
  # stand = TRUE,
  # covs = TRUE,
  digits = 3,
  stars = "regress"
)

save_png(
  plot_long_M1M2M3M4,
  "~/Documents/KateTran_Github/ABCD_covid/plots/mediator_longitudinal/plot_long_M1M2M3M4.png"
)
```